Millions of Type Errors

### 2023-08-25 programming23/paper.tex
quick note, data model
note, big edit range
note about cutoff, not sure if right idea

FILL ignore sessions close to start / end time?
remove all syntax errors from later stages?

@@

@@

>>>>

Edit range ignore huge numbers (above 4B),
which are the result of subtraction overflowing.
%% 4,000,000,000

Sessions, ignore if too close to start or end.
Deciding if a session is close is tricky because we don't have
a firm start and end time.
Um, does this make sense at all?
Well anyway we took the greater number from mean vs median
gap (over all points, not just keystroke points)
and multiplied by Nx to test closeness to a boundary.
With N=2 we drop 1 nonstrict session, 0 strict (not sure about nocheck).
With N=4 we drop 3, with N=8 we drop 9.

FILL remove all syntax errors from later stages?

@@

Seventh,

\begin{figure}[t]
  \includegraphics[width=0.8\columnwidth]{img/example-compass.png}
  \caption{Are there fewer type errors than forcedstrict errors? Expect true always, but that is not the case.}
  \label{f:tefs}
\end{figure}

@@

\Cref{f:scribbles} kill this.

\subsection{Asset Creation vs Scripting}

Data model. Point to discussion above.

Big fluctuations in errors.
FS disagrees with TE.
Probably data model!
